IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-03 assets/waveform_wpt_modulated.tex
:bento: Update assets

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,3.312in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213595499958\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	4.47213595499958\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

@@

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,2.598in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	3.16127375477314\\
2	3.16328124696217\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	3.16000164000459\\
2	3.16455204336543\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,1.883in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=4.47213595499958,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	2.23287518822941\\
2	2.2349269985345\\
3	2.23712082213722\\
4	2.2393436833526\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.23243942623434\\
2	2.23535811809091\\
3	2.23559687073864\\
4	2.24086923394096\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,1.168in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.56947570711734\\
2	1.57851757716824\\
3	1.58044033841813\\
4	1.58155392693919\\
5	1.58198101788601\\
6	1.58501068613205\\
7	1.5854415059255\\
8	1.58662414938375\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.56539227519679\\
2	1.57784161002588\\
3	1.57927371173129\\
4	1.58176667731984\\
5	1.58367655185228\\
6	1.58456745246925\\
7	1.58798555735369\\
8	1.58848608357287\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,0.454in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.10024627987476\\
2	1.10664679147412\\
3	1.11204358490005\\
4	1.11548794498246\\
5	1.11636022580843\\
6	1.11667878555116\\
7	1.11706894724375\\
8	1.11773783143934\\
9	1.11958645829829\\
10	1.12088764958973\\
11	1.1221919201651\\
12	1.12315337822569\\
13	1.12435794296855\\
14	1.12469670812645\\
15	1.12549793104218\\
16	1.12556826383419\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.09504669861652\\
2	1.10317579191466\\
3	1.11227601228037\\
4	1.11361418816502\\
5	1.11483774301138\\
6	1.11656722620907\\
7	1.11743910790233\\
8	1.11769734992669\\
9	1.11854798737502\\
10	1.12003038718696\\
11	1.12377646668063\\
12	1.12467567262626\\
13	1.12655148101693\\
14	1.1274126433068\\
15	1.12796634097065\\
16	1.12836437582839\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,3.251in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=5,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213595034367\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	4.47213593685897\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

@@

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,2.553in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=5,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.000570870326956724\\
2	4.4721359179404\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.0110856763978608\\
2	4.47212221176042\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,1.855in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=5,
ytick={0, 2, 4},
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.82810775851695e-05\\
2	3.53085892593064e-05\\
3	3.54347120351704e-05\\
4	4.42555930751421\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.22676166428777e-05\\
2	2.19662118918467e-05\\
3	2.35611473414708e-05\\
4	4.38314990531919\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,1.157in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=1,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	6.25263040326118e-06\\
2	6.27921380470113e-06\\
3	6.34955721457943e-06\\
4	6.35150273149039e-06\\
5	6.42390701416729e-06\\
6	6.42457974220412e-06\\
7	6.47741859691329e-06\\
8	6.47969375628299e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.07597912435039e-05\\
2	2.10621157490525e-05\\
3	2.27177871268911e-05\\
4	2.34764127724776e-05\\
5	0.000633429285281999\\
6	0.00299168089473067\\
7	0.0168627108170759\\
8	0.0302609478988545\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=1,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.46841221768753e-06\\
2	1.46853581584948e-06\\
3	1.46888556831603e-06\\
4	1.46960879811052e-06\\
5	1.47063822579491e-06\\
6	1.47112726920342e-06\\
7	1.47158812622008e-06\\
8	1.47177039924161e-06\\
9	1.47273523214333e-06\\
10	1.47288042283048e-06\\
11	1.47389962773962e-06\\
12	1.47396082891411e-06\\
13	1.47467419234042e-06\\
14	1.47476166458671e-06\\
15	1.47506643379659e-06\\
16	1.47509099313304e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.08632407458004e-05\\
2	1.08877007745949e-05\\
3	1.09594364217047e-05\\
4	1.10938027865036e-05\\
5	1.12827891666553e-05\\
6	1.15378065652616e-05\\
7	1.19617266900702e-05\\
8	1.41613520483063e-05\\
9	6.92466622068608e-05\\
10	0.000224790946436711\\
11	0.000536194940235116\\
12	0.0020179447121528\\
13	0.00228142595005787\\
14	0.00484194141261625\\
15	0.00509975660438143\\
16	0.00611499201390601\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

### 2021-08-03 assets/waveform_wpt_multisine.tex
:bento: Update assets

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,3.312in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	0.000331092582051402\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{P}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	0.000301200841788861\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No IRS: {\boldmath${s}$}$_{\mathrm{P}}$}

@@

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,2.598in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	8.31476170438795e-06\\
2	8.59623838841982e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.51350625686209e-05\\
2	2.5738452816653e-05\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,1.883in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=4.47213595499958,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.81401011150761e-05\\
2	7.63567990520219e-05\\
3	0.000347720308108743\\
4	1.20961154306659\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.00111014489403298\\
2	0.00243652079053788\\
3	0.00358274270606404\\
4	1.61181535442991\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,1.168in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.406193755485101\\
2	0.6086191375554\\
3	0.70781380097226\\
4	1.11700551493449\\
5	1.39413019214519\\
6	1.89924922357725\\
7	2.27606557910904\\
8	2.64280256661518\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.621345098069754\\
2	0.710296651693143\\
3	0.908023988477654\\
4	1.12050035456782\\
5	1.44244708781013\\
6	1.77492365099369\\
7	2.30702814170141\\
8	2.53638471775812\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,0.454in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.280439553353647\\
2	0.384605443069534\\
3	0.416114603863305\\
4	0.499024317224016\\
5	0.571268128602638\\
6	0.621900186283823\\
7	0.763344617968865\\
8	0.858693319856245\\
9	0.954356161751161\\
10	1.16907743761735\\
11	1.21561270661726\\
12	1.45089690540298\\
13	1.51204499963039\\
14	1.68681223326519\\
15	1.74569476977388\\
16	1.81071246294588\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.447567787711277\\
2	0.504906671531525\\
3	0.589458291557858\\
4	0.619646960375962\\
5	0.691059903147371\\
6	0.741736916016998\\
7	0.810826698348076\\
8	0.887751406400927\\
9	0.941910732226763\\
10	1.15698606523739\\
11	1.20259880483264\\
12	1.42353667332449\\
13	1.46532152628089\\
14	1.65027292091107\\
15	1.65828648619566\\
16	1.73730645060792\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,3.198in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=1,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	0.000179640013528533\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{P}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	0.000397123673947016\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No IRS: {\boldmath${s}$}$_{\mathrm{P}}$}

@@

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,2.513in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=1,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	3.79500700797208e-06\\
2	4.08912055500049e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.49290916575988e-05\\
2	1.5984007495811e-05\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.828in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=1,
ytick={0, 1},
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.7047574186968e-05\\
2	5.43653691324513e-05\\
3	5.45654270177953e-05\\
4	0.643758338055473\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.36848368645437e-05\\
2	2.47445070835246e-05\\
3	2.69448998495505e-05\\
4	0.887691893042722\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.143in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.0867788582585271\\
2	0.354584687432597\\
3	0.978311956865194\\
4	1.00526014633142\\
5	1.77421254564815\\
6	1.81146146011329\\
7	2.39316922290828\\
8	2.39637542235877\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.0902176300392888\\
2	0.346545381997116\\
3	0.920392715728033\\
4	1.00603974348273\\
5	1.68636658487784\\
6	1.88211529376329\\
7	2.36040788303805\\
8	2.46040714408403\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.0464370103565898\\
2	0.0888998754115983\\
3	0.182477468723257\\
4	0.351067698858224\\
5	0.586511157963407\\
6	0.614337078252067\\
7	0.810319773242887\\
8	0.860994249853337\\
9	1.10132170987082\\
10	1.14707079761106\\
11	1.39883656543765\\
12	1.41535986846215\\
13	1.61724209266044\\
14	1.62252465458191\\
15	1.72749872908311\\
16	1.73005229015507\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.0510852453116461\\
2	0.0931309188028207\\
3	0.185327611314329\\
4	0.340208570070271\\
5	0.54797982875002\\
6	0.640935330786823\\
7	0.791412536150533\\
8	0.84579943866006\\
9	1.06112099796475\\
10	1.16793555562456\\
11	1.33939925851288\\
12	1.47707717171709\\
13	1.57685904146789\\
14	1.6756197826186\\
15	1.71965928671636\\
16	1.75172173644803\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%
